Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
Small corrections everywhere
Fix Fig 3 entry block + extend its caption.
Fix wrong commit

Directories contain lists of people with various information attached.
For instance, the directory published by \emph{Didot} in 1854 contains three redundant lists of people sorted by name, by activity and by street name.
A typical example entry from this directory is "\textit{Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47.}".
It begins with the person's name and surname, here inside parentheses.
The glyph denotes that this person was awarded the \textit{Légion d'Honneur}.
Then comes a description of the person's activity, here his profession (professor at the Conservatory of music and declamation), but it can also be a social status.
Such descriptions range from a single word to paragraphs describing the occupation in full detail.
The street name and number where the person lives or carries out their activities ends the entry.

@@

%\joseph{TODO: separate entry detection, OCR and NER stages explicitely}

@@

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. An OCR system runs
on the thumbnails of each segmented entry to extract its text. An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). The glyphs used in this dataset might be unknown to the OCR. Some of them, like
\scalerel*{\includegraphics{./images/LH.png}}{H}, do not even have a Unicode codepoint. Text normalisation is thus required
on the OCR outputs and consists in projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes
sense), homogenise extra symbols (star and hand symbols), and alleviate some ambiguities (e.g. \emph{no} and \emph{n°}).

At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed.

%\joseph{[DONE] a word about the charset, and existence of glyphs unknown to the OCR}
%\joseph{[DONE] parler de l'étage d'extraction d'entrées qui est validé manuellement, et des quelques règles de simplification du charset pour homogénéiser entre les annotateurs / pallier des ambiguïtés dans les règles d'annotation (qu'on pourrait encore améliorer)}

@@

Note that the dataset used to assess the NER stage is a subset of the entries. Indeed, we need to ensure that the datasets
contain the same entries whichever the OCR used in the previous stage. Entries where the OCR produced an empty string
and those for which no entity could be projected from the groundtruth have to be ignored. We filter the set of entries by
keeping only the entries that are always valid at the end of stage 1. At the cost of losing 5\% of the references
entries, we thus have 8341 valid entries at the input of stage 2.

@@

% It can therefore be used to train and improve the entry detection, OCR and NER tools.
% book, page, box, text_ocr, ner_xml (+uid within a page)

%\joseph{TODO intégrer dans les sections avant ?}
%
%
% valid ner (ref \& pero \& tess): 8341
%
%TODO average entry len (in char)
%TODO average number of tags/entities per entry
%TODO lists actual dataset content: set of entries. For each entry:
%\begin{itemize*}
%    \item ref to original book, page, region
%    \item human transcription (OCR GT)
%    \item human NER (NER GT)
%    \item [GENERATED] OCR produced by Pero OCR, Tesseract v4, Kraken (precise model used)
%    \item [GENERATED] NER GT aligned on text predictions from Pero OCR, Tesseract v4, Kraken
%\end{itemize*}

%\joseph{TODO expliquer qu'il faut faire la fusion des sous-datasets NER}

%\subsection{Focus on how NER GT was aligned on noisy OCR}

@@

\textbf{OCR Q.A.}  The predicted text by the OCR system is aligned with the groundtruth text using standard tools from
Stephen V. Rice's thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip}. The Character Error Rate (CER) is computed at
the entry level and at the global level, defined as the ratio between the number of errors
(insertions/deletions/substitutions) over the reference text length.

@@

The evaluation process is illustrated on~\cref{fig.eval-ocr-ner}. The OCR and the groundtruth texts are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.
%
A side effect of tag projection is that it can produce degenerated tags, i.e., empty or containing only spaces.
In such cases, the corresponding entries must be removed from the dataset,
and only the intersection of the sets of valid entries must be used to compare NER systems with multiple OCR predictions or references.

>>>>

Directories contain lists of people with various information attached.
For instance, the directory published by \emph{Didot} in 1854 contains three redundant lists of people sorted by name, by activity and by street name.
A typical example entry from this directory is ``\textit{Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47.}''.
It begins with the person's name and surname, here inside parentheses.
The glyph denotes that this person was awarded the \textit{Légion d'Honneur}.
Then comes a description of the person's activity, here his profession (professor at the Conservatory of music and declamation), but it can also be a social status.
Such descriptions range from a single word to paragraphs describing the occupation in full detail.
The street name and number where the person lives or carries out their activities ends the entry.

@@

@@

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. An OCR system runs
on the thumbnails of each segmented entry to extract its text. An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). 
Some glyphs used in this dataset might be unknown to the OCR, and some like
\scalerel*{\includegraphics{./images/LH.png}}{H} do not even have a Unicode codepoint, and were annotated using Unicode Private User Area 1.
Furthermore, as some annotations guidelines where unclear to human annotators, some projections rules were applied: whitespace, dash, dots and a couple of commonly confused characters where projected to well-defined codepoints.
The same normalization was applied to OCR predictions.
At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed on the basis of the $8,765$ entries which were manually controlled, totalling $424,764$ characters (including $54,387$ spacing characters). Entries are $49.0$-characters long on average.

@@

Note that the dataset used to assess the NER stage is a subset of the entries. Indeed, we need to ensure that the datasets
contain the same entries whichever the OCR used in the previous stage. Entries where the OCR produced an empty string
and those for which no entity could be projected from the groundtruth have to be ignored. 
We filter the set of entries by keeping only the entries that are always valid at the end of the stage 1.
%At the cost of losing 5\% of the references entries, we thus have 8341 valid entries at the input of the stage 2.
% /!\ True only for \peroocr and Tesseract predictions, not considering Kraken (we loose 500 more entries)
Therefore, the $8,765$ reference entries were manually annotated with $34,242$ entities; entries contain $3.9$ entities on average.
Projecting reference tagged entities on OCR predictions resulted in a variable loss of entries.
For \peroocr, $8,392$ valid entries were generated, for Tesseract $8,700$ and for Kraken $7,990$.
The resulting intersection of the sets of valid entries contained $7,725$ entries for the tree OCR systems (and the reference),
or $8,341$ entries if we consider \peroocr and Tesseract only.

@@

%
%TODO average number of tags/entities per entry
%TODO lists actual dataset content: set of entries. For each entry:
%\begin{itemize*}
%    \item ref to original book, page, region
%    \item human transcription (OCR GT)
%    \item human NER (NER GT)
%    \item [GENERATED] OCR produced by Pero OCR, Tesseract v4, Kraken (precise model used)
%    \item [GENERATED] NER GT aligned on text predictions from Pero OCR, Tesseract v4, Kraken
%\end{itemize*}

@@

\textbf{OCR Q.A.}  The predicted text by the OCR system is aligned with the groundtruth text using standard tools from
Stephen V. Rice's thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip}. The Character Error Rate (CER) is computed at
the entry level and at the global level, defined as the ratio between the number of errors
(insertions/deletions/substitutions) over the reference text length.
Word Error Rate is hard to define for our tokens and was not considered.

@@

The evaluation process is illustrated on~\cref{fig.eval-ocr-ner}. The OCR and the groundtruth texts are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.
%
% A side effect of tag projection is that it can produce degenerated tags, i.e. empty or containing only spaces.
% In such cases, the corresponding entries must be removed from the dataset,
% and only the intersection of the sets of valid entries must be used to compare NER systems with multiple OCR predictions or references.
